Impact of Training Variability on Visuomotor Function Learning and Extrapolation

### 2024-05-20 Sections/Intro.qmd
remove other hugo files

[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"}\

[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}

[repo](https://github.com/tegorman13/htw){target="_blank"} \

>>>>

{{< fa file-lines >}} [Link to project page](https://tegorman13.github.io/htw/){target="_blank"} \

{{< fa file-pdf >}} [Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}

{{< fa brands github >}} [repo](https://github.com/tegorman13/htw) \
